### 2020-12-06 paper/localpsf.tex
edits to poiwwon weighting functions section

A key advantage of Poisson interpolation over other PSF interpolation methods, most notably radial basis functions [cite Escande etc], is that Poisson interpolation is \emph{geometry-aware}---Poisson interpolation incorporates information about the domain geometry when constructing the weighting functions. Consider the Pine island glacier geometry shown in Figure REF. Regions of the glacier are separated by thin inlets of ocean. With radial basis function interpolation, PSF samples on one side of the inlet inappropriately influence the interpolation on the other side of the inlet. With Poisson interpolation, the PSF samples only influence the interpolation on their own side of the inlet.

>>>>

A key advantage of Poisson interpolation over other PSF interpolation methods, most notably radial basis functions [cite Escande etc], is that Poisson interpolation incorporates information about the domain geometry when constructing the weighting functions. Consider the Pine island glacier geometry shown in Figure REF. Regions of the glacier are separated by thin inlets of ocean. With radial basis function interpolation, PSF samples on one side of the inlet inappropriately influence the interpolation on the other side of the inlet. With Poisson interpolation, the PSF samples only influence the interpolation on their own side of the inlet.
